Output Approximation for PHP at Scale:\\ Experience and Analysis

### 2017-02-04 paper.tex
first draft
revised related work

\begin{document}
\title{Does It Scale? Symbolic Execution of PHP Web Applications}
%\titlenote{Produces the permission block, and copyright information}
%\subtitle{Output-oriented Symbolic Execution for Static Output Approximation}
%\subtitlenote{The full version of the author's guide is available as  \texttt{acmart.pdf} document}

@@

\section{Conclusion}
In this paper we have addressed symbolic execution of PHP web applications that
is used for client page output approximation. These approximations are leveraged
be several developer tools for PHP that yet have not been evaluated for larger
systems. We re-implemented and extended an existing symbolic execution engine
to analyze several real-world PHP applications with the intention to evaluate
the scalability of symbolic execution for PHP. Our work illustrates the
necessity of more comprehensive evaluation of developer tools as
symbolic execution is a conceptually suitable, but not necessary practical
approach to approximate client page output. Dynamic features of PHP in
combination with symbolic values though can hinder precise symbolic execution
and limit the scalability and practicality of tools relying on symbolically
approximated output.

@@

%\newpage
%References
\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

>>>>

\begin{document}
%\title{Does It Scale? Symbolic Execution of PHP Web Applications}
\title{Output Approximation for PHP at Scale:\\ Experience and Analysis}
%\titlenote{Produces the permission block, and copyright information}
%\subtitle{Output-oriented Symbolic Execution for Static Output Approximation}
%\subtitlenote{The full version of the author's guide is available as  \texttt{acmart.pdf} document}

@@

\section{Conclusion}
In this paper we have addressed symbolic execution of PHP web applications that
is used for client page output approximation. These approximations are leveraged
be several developer tools for PHP that yet have not been evaluated for larger
systems. We re-implemented and extended an existing symbolic execution engine
to analyze several real-world PHP applications with the intention to evaluate
the scalability of symbolic execution for PHP. Our work illustrates the
necessity of more comprehensive evaluation of developer tools as
symbolic execution is a conceptually suitable, but not necessary practical
approach to approximate client page output. Dynamic features of PHP in
combination with symbolic values can hinder precise symbolic execution
and limit the scalability and practicality of tools relying on symbolically
approximated output.

@@

%\newpage
%References
\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography,dblp2_short,tien}

### 2017-02-04 related.tex
revised related work

Wang {\em et al.}~\cite{wang-fse12}'s approach executes the
(instrumented) server-side code with a specific input to generate the
client code. Changes in that generated code can then be mapped to
their origins in the PHP code using the recorded run-time mappings and
static impact analysis.
%We similarly track origin locations, but we symbolically execute the
%PHP code.
%
%We previously used our symbolic execution engine \emph{PhpSync} for
%similar purposes~\cite{drc-ase13,phpsync}. First, we 
PHPSync~\cite{phpsync} used static origin tracking to propagate
changes in the client code (output of symbolic execution) back to the
PHP code. Subsequently, the same authors designed DRC to analyze both
PHP code and generated client-side code to detect cross-language and
cross-stage dangling references~\cite{drc-ase13}. DRC matches path
constraints of references/declarations without fully symbolic
execution. It uses the path conditions from symbolic execution to
determine in which configurations dangling references can occur.

Apollo~\cite{artzi-icse10,artzi-tse10}, a more general fault
localization tool for PHP code, rates the PHP echo/print
statements higher in suspiciousness by running an instrumented
interpreter on test cases. Clark {\em et al.}~\cite{clark-ase11}
localize faults in an SQL command embedded within JSP code.

@@

Another approach is proposed by Wang et al. \cite{wang_automating_2012}, where
output for a web application is approximated using a hybrid approach: A
dynamic web page is executed with concrete input and the execution is
recorded at run-time. Changes in the client-side output then can be mapped to 
corresponding PHP code using static impact analysis.

@@

\paragraph{Dynamic Features}
According to a case study by Hills et al. \cite{Hills:2013:ESP:2483760.2483786}
of the feature usage in PHP, based on a corpus of state-of-the-art-projects,
dynamic includes are less frequently used than static includes, yet usage
frequency varies from system to system. Further work by Hills et al.
\cite{hills2014static,hills2014php} approaches static resolution of dynamic includes using
both context-insensitive resolution on file level by simplifying PHP constants;
and context-sensitive on program level for transitive includes. In spite of 
promising results, these approaches, similar to our results, face limitations
for truly dynamic includes if resolution is not sound due to information not
being available in the source code like database query results.

>>>>

Wang {\em et al.}~\cite{wang-fse12}'s approach executes the
(instrumented) server-side code with a specific input to generate the
client code. Changes in that generated code can then be mapped to
their origins in the PHP code using the recorded run-time mappings and
static impact analysis.
%We similarly track origin locations, but we symbolically execute the
%PHP code.
%
%We previously used our symbolic execution engine \emph{PhpSync} for
%similar purposes~\cite{drc-ase13,phpsync}. First, we 
PHPSync~\cite{phpsync} used static origin tracking to propagate
changes in the client code (output of symbolic execution) back to the
PHP code. Subsequently, the same authors designed DRC to analyze both
PHP code and generated client-side code to detect cross-language and
cross-stage dangling references~\cite{drc-ase13}. DRC matches path
constraints of references/declarations without fully symbolic
execution. It uses the path conditions from symbolic execution to
determine in which configurations dangling references can occur.
%
Apollo~\cite{artzi-icse10,artzi-tse10}, a more general fault
localization tool for PHP code, rates the PHP echo/print
statements higher in suspiciousness by running an instrumented
interpreter on test cases. Clark {\em et al.}~\cite{clark-ase11}
localize faults in an SQL command embedded within JSP code.

@@

In another approach by Wang et al. \cite{wang_automating_2012}, 
output for a web application is approximated using a hybrid approach: A
dynamic web page is executed with concrete input and the execution is
recorded at run-time. Changes in the client-side output then can be mapped to 
corresponding PHP code using static impact analysis.

\paragraph{Dynamic Output Approximation}
Zou {\em et al.}~\cite{zou-issta14} introduce a V-DOM coverage for web
applications. They convert a PHP program into C code and performs
static analysis for control flows and data flows to build a V-DOM
tree. V-DOM coverage is defined as the ratio of the number of covered
DOM objects over the total number of DOM
objects. DomCovery~\cite{mesbah-issta14} is another DOM-based coverage
criteria for web applications. The coverage is defined at two levels:
(1) the percentage of DOM states and transitions covered in the total
state space, and (2) the percentage of elements covered in each
particular DOM state.

@@

\paragraph{Dynamic Features in Web applications}
According to a case study by Hills et al. \cite{Hills:2013:ESP:2483760.2483786}
of the feature usage in PHP, based on a corpus of state-of-the-art-projects,
dynamic includes are less frequently used than static includes, yet usage
frequency varies from system to system. Further work by Hills et al.
\cite{hills2014static,hills2014php} approaches static resolution of dynamic includes using
both context-insensitive resolution on file level by simplifying PHP constants;
and context-sensitive on program level for transitive includes. In spite of 
promising results, these approaches, similar to our results, face limitations
for truly dynamic includes if resolution is not sound due to information not
being available in the source code like database query results.
